Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2023-03-15 src/tex/ms.tex
[showyourwork] overleaf sync

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{multirow}
\usepackage{nicefrac}
\usepackage{wasysym}
\usepackage{amssymb}

@@

>>>>

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{multirow}
\usepackage{nicefrac}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage[inline]{enumitem}

@@

\begin{figure}
    \script{wg_IV_risks.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/wg_IV_risks.png}
        \caption{Distributions over the risk for microscopic involvement in \gls{lnl} IV as predicted by the winning graph model, given early (top panel) or late T-category (bottom panel), and three different CT-based diagnoses:
        \begin{enumerate*}[label=\arabic*)]
            \item A clinical N0 patient (gray histogram),
            \item visible metastases in \gls{lnl} II, but otherwise healthy-looking lymph nodes (blue histogram), and
            \item macroscopic metastases in the \glspl{lnl} II \& III, whith the rest of the neck still being clinically ode negative (orange histogram).
        \end{enumerate*}
        }
        \label{fig:wg_IV_risks}
    \end{centering}
\end{figure}

\begin{figure}
    \script{wg_V_risks.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/wg_V_risks.png}
        \caption{The winning graph's predictions over the risk for occult disease in \gls{lnl} V for early (top panel) and late T-category (bottom panel). Each of the risks is computed, given one of three diagnostic scenarios that were obtained by a CT scan:
        \begin{enumerate*}[label=\arabic*)]
            \item A clinically healthy neck (green),
            \item on CT imaging visible involvement in the \glspl{lnl} II \& III (orange) with the remaining levels still clinically negative, and
            \item observed involvement in the levels II, III, and IV (red).
        \end{enumerate*}}
        \label{fig:wg_V_risks}
    \end{centering}
\end{figure}
